Exploring dimensions of biodiversity in Japanese ferns

### 2021-08-30 ms/manuscript.Rmd
Fix combining forest PAs with other PAs
Make sure medium and high levels don't overlap

# Calculate baseline protection percentage: percent protected areas across the whole country
total_percent_protected <-
  protected_areas %>%
  as_tibble() %>%
  select(-geometry) %>%
  filter(status %in% c("medium", "high")) %>%
  group_by(status) %>%
  summarize(
    total_area = sum(area),
    .groups = "drop"
  ) %>%
  mutate(percent_protected = total_area/area_of_japan) %>%
  mutate(percent_protected = as.numeric(percent_protected))

>>>>

# Calculate baseline protection percentage: percent protected areas across the whole country
total_percent_protected <-
  protected_areas %>%
  mutate(area = st_area(.) %>% units::set_units(km^2)) %>%
  as_tibble() %>%
  select(-geometry) %>%
  filter(status %in% c("medium", "high")) %>%
  group_by(status) %>%
  summarize(
    total_area = sum(area),
    .groups = "drop"
  ) %>%
  mutate(percent_protected = total_area/area_of_japan) %>%
  mutate(percent_protected = as.numeric(percent_protected))
